Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-09-19 draft/draft0.tex
updates

In \cite{Li2014,Li2015,Li2016} we proposed a series of methods to probe the geometric information encoded in the LSS data.
We make use of the fact that the AP or volume effect commonly introduce redshift-dependent geometric distorion in the LSS,
which can be distinguished from the other effects such as the redshfit space distortion (RSD).
RSD arises because the radial distances of galaxies are inferred from redshifts which is contaminated by the pecular motion of galaxies, 
leading to apparent anisotropy even if the adopted cosmology is correct \citep{Ballinger1996}.
RSD is the usually main caveats for probe geometry using LSS,
and we found it can be largerly avoid by focusing on the the redshift dependence of the anisotropy.

\cite{Li2014} proposed used the {\it galaxy density gradient field} 
to characterize the anisotropies in LSS and tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing the redsift evolution of the gardient field can be used to infer unbiased constraints cosmological parameters and is insensitive to RSD.
The same topic was revisited in \cite{Li2015}, but using the statistical tool of {\it galaxy two-point correlation function} (2pCF) as a function of angle, $\xi(\mu)$.
When incorrect cosmological parameters are adopted, the shape of $\xi(\mu)$ appears anisotropic due to the AP effect, 
and the amplitude is shifted by the change in comoving volume;
both effects have significant redshift dependence.
The RSD effect, although significantly distorting $\xi(\mu)$, 
exhibits much less redshift evolution compared to the effect coming from incorrectly adopted cosmologies.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of AP effect and lead to tight cosmological constraints.

We developed a method measuring the redshift of the shape of galaxy angular correlation function to constrain cosmology.
A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
which leads to redshift-dependent change in the angular 2pCF shape.
The signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We test our method on the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2.
Analyzing redshift evolution of the shape of 2pCF on scales $5 - 40 h^{-1} {\rm Mpc}$, we derive tight constraints on $\Omega_m$ and $w$.

In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
%The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
%We hope this method also.
%The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
%Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
which shifts apparent scale of the clustering patterns;
this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We test our method on the HR4 mock galaxies.
The method can be applied to current and future LSS surveys,
especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.

The outline of this paper proceeds as follows. 
In \S 2 we briefly review the nature and consequences of the geometric distortion in LSS when performing coordinate transforms in a cosmological context. 
In \S 3 we describe the mock galaxies produced from N-body simulations which are used to test our methodology.
The methodology is presented in \S 4.
We conclude in \S 6.

>>>>

In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
%proposed a series of methods to probe the geometric information encoded in the LSS data.
We found fact that the AP or volume effect in general introduces a geometric distortion significantly evolves with redshift;
this phenomenon can be utilized to distinguish the the from the other effects such as the redshift space distortion (RSD).
The radial distances of galaxies are inferred from the measured redshifts which are distorted by the peculiar motion of galaxies, 
leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
It is the major systematic effects limiting our ability to probe the geometry of LSS from galaxy distribution.
We found its influence is significantly reduced in case of studying the redshift dependence of the distortion.

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing the redshift evolution of the statistical property of the gradient field 
can be used to infer unbiased constraints cosmological parameters and is insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using the statistical tool of {\it galaxy two-point correlation function} (2pCF) as a function of angle, $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the direction.
When incorrect cosmological parameters are adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic shape of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the size of comoving volume;
both effects have significant redshift dependence.
The RSD effect, although {\it very significantly} distorts $\xi(\mu)$, 
exhibits less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of the AP effect, 
and we come up with tight cosmological constraints comparable to the mainstream probes of SNIa, BAO, CMB and so on.

In this paper we continue our exploration of our strategy and presented 
a new method using the redshift of the shape of {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2
and develop the statistical procedure to constrain cosmological parameters.

%In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
%The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
%We hope this method also.
%The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
%Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
%A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
%which shifts apparent scale of the clustering patterns;
%this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
%We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
%the galaxy bias, and the RSD effect.
%We test our method on the HR4 mock galaxies.
%The method can be applied to current and future LSS surveys,
%especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.

The outline of this paper proceeds as follows. 
In \S 2 we briefly review the nature and consequences of the LSS geometric distortion when performing coordinate transforms in a cosmological context. 
In \S 3 we describe the N-body mock galaxies used to test our method.
The methodology is presented in \S 4.
We conclude in \S 5.
